%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj, Modified: Karl Pertsch
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex, hidelinks]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-0pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-0pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeDatedItem}[3]{
	\vspace{-1pt}\item{
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\small{\textbf{#1}#2} & \small{#3}
	\end{tabular*}\vspace{-20pt}
}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Karl Pertsch}} (Updated Sept 2017) & Email : \href{mailto:pertsch@usc.edu}{pertsch@usc.edu}\\
  \href{https://kpertsch.github.io}{kpertsch.github.io}& \\%Mobile : +1-(215)-285-6360 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Pennsylvania}{Philadelphia, PA}
      {Fulbright Visiting Scholar in Computer Science;  GPA: 4.0 (Fall 2017 term)}{Aug. 2017 -- May 2018}
    \resumeSubheading
      {Technical University Dresden}{Dresden, Germany}
      {Diploma in Electrical Engineering, Focus: Robotics and Control;  GPA: 4.0 (with distinction)}{Aug. 2012 -- Aug. 2017}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

	\resumeSubheading
	{GRASP Lab, University of Pennsylvania}{Philadelphia, PA}
	{Fulbright Visiting Scholar, Supervisor: Kostas Daniilidis}{Aug. 2017 - May 2018}
	\resumeItemListStart
	\resumeItem{Unsupervised Activity Recognition}
	{Learn a viewpoint-independent embedding that discriminates actions of birds in video data without human training annotations.}
	\resumeItem{Coursework}
	{Take classes in deep learning for computer vision (instructor: Jianbo Shi) and reinforcement learning. Final projects investigate GANs for data augmentation and Generative Adverserial Imitation Learning.}
	\resumeItemListEnd

    \resumeSubheading
      {Computer Vision Lab Dresden}{Dresden, Germany}
      {Diploma Thesis, Supervisor: Carsten Rother}{Apr. 2017 - Aug. 2017}
      \resumeItemListStart
        \resumeItem{Object Pose Estimation}
          {Design, implement and test a pipeline for 6DoF pose estimation of objects from single RGB/RGB-D input images. Used dataset features texture-less objects and heavy occlusion.}
        \resumeItem{Deep Learning}
          {Implement Deep CNNs in Caffe for instance-aware semantic segmentation and 3D shape reconstruction as part of the pose estimation pipeline.}
      \resumeItemListEnd

    \resumeSubheading
      {Institute of Automotive Engineering Dresden}{Dresden, Germany}
      {Research Assistant}{Apr. 2016 - Jan. 2017}
      \resumeItemListStart
        \resumeItem{Reinforcement Learning}
          {Develop a Reinforcement Learning algorithm for learning energy-optimal driving strategies for hybrid-electric vehicles. Implementation of linear value function approximation for improved learning speed and accuracy.}
      \resumeItemListEnd

    \resumeSubheading
      {BMW Research and Technology}{Munich, Germany}
      {Research Intern}{Oct. 2015 - Mar. 2016}
      \resumeItemListStart
        \resumeItem{Data Acquisition}
          {Develop tools for data acquisition and evaluation in ROS for learning-based techniques in the field of automated driving.}
        \resumeItem{Maneuver Classification and Prediction}
          {Develop machine learning algorithms for the classification and prediction of vehicle lane change maneuvers using TensorFlow.}
      \resumeItemListEnd

    \resumeSubheading
      {Technical University Dresden}{Dresden, Germany}
      {Teaching Assistant}{Apr. 2014 - Mar. 2015}
      \resumeItemListStart
        \resumeItem{Algebra and Electrical Engineering}
          {Independently held two weekly exercises in undergraduate mathematics for engineers and lead the extra-tuition program in electrical engineering for undergraduate students.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Scholarships and Awards}
  \resumeSubHeadingListStart
    \resumeDatedItem{Fulbright Scholarship}{: Awarded by the US government for academic excellence and social commitment.}{Aug. 2017}
    \resumeDatedItem{Year's Best Pre-Diploma}{: Awarded by the Faculty of Electrical and Computer Engineering.}{Aug. 2014}
    \resumeDatedItem{Deutschlandstipendium}
      {: National scholarship for outstanding academic achievements.}{Oct. 2013 - Sep. 2017}
  \resumeSubHeadingListEnd
\vspace{7px}
%
%--------PROGRAMMING SKILLS------------
%\section{Technical Skills}
%  \resumeSubHeadingListStart
%    \item{\textbf{Languages}{: C++, Python, Matlab, Java/Android}}
%    \vspace{-7px}
%    \item{\textbf{Technologies}{: Caffe, TensorFlow, ROS, Matlab/Simulink}}
%  \resumeSubHeadingListEnd
  
%--------PUBLICATIONS------------------
\section{Publications}
\hangindent+30pt \hangafter=1
O. H. Jaffari*, S. K. Mustikovela*, \textbf{K. Pertsch}, E. Brachmann, C. Rother, 'The best of both worlds: learning geometry-based 6D object pose estimation', submitted to \textit{Conference on Computer Vision and Pattern Recognition (CVPR)}, 2018.

\hangindent+30pt \hangafter=1
\textbf{K. Pertsch}, R. Liessner, B. Baeker, 'Reinforcement learning as a means for future diagnostical techniques',\hspace{2cm} (published in German) \textit{11\textsuperscript{th} Conference on Diagnosis in Mechatronic Vehicle Systems}, 2017.


%-------------------------------------------
\end{document}
